---
title             : "Some Long Title - Maybe something more specific"
shorttitle        : "Short Title"

author: 
  - name          : "Author 1"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Street Str. 1"
    email         : "author.one@mail.com"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - "Conceptualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - name          : "Author 2"
    affiliation   : "2"
    role:
      - "Supervision"

affiliation:
  - id            : "1"
    institution   : "Ruprecht-Karls-University Heidelberg"
  - id            : "2"
    institution   : "Konstanz Business School"
  # add a second id using this syntax

authornote: |
  Author Notes go here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  
  One or two sentences to put the results into a more **general context**.
  
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keyword, more keyword, crazy keyword"
wordcount         : "X"

# bibliography      : ["r-references.bib"] # put your ref files here

floatsintext      : yes # for pics in text
linenumbers       : no
draft             : no
mask              : no

figurelist        : no
tablelist         : no
footnotelist      : no
link-citations    : true # custom addin, makes citations link to reference section
# figsintext        : yes # custom addin

classoption       : "man"
# the settings below allow compilation of APA7 style citations/documents
header-includes:
  - |
    \makeatletter
    \renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
      {-1em}%
      {\normalfont\normalsize\bfseries\typesectitle}}
    
    \renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
      {-\z@\relax}%
      {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
    \makeatother
  - | 
    \raggedbottom
  - |
    \usepackage{hhline}
  - |
    \setlength{\parskip}{0pt}

csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass     : "apa7"
output            : papaja::apa6_pdf
---
```{r setup, include = FALSE}
# Working directory
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

# disallow tables breaking over pages
knitr::opts_chunk$set(ft.keepnext = TRUE,
                      ft.align = "left",
                      ft.latex.float = "float")
# Seed for random number generation
set.seed(1234)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed) # this adds random seed to all chunks
knitr::opts_chunk$set(autodep = TRUE)
knitr::opts_chunk$set(message = FALSE)

knitr::dep_auto()
```

<!-- Setup -->
```{r setup-libraries}
# think about calling renv here to make sure everyone has the same packages installed
list.of.packages <- c("tidyverse", "rmarkdown", "papaja", "knitr", "psych")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

library(papaja)
library(tidyverse)
library(rmarkdown)
library(knitr)
library(psych)
library(readxl)

r_refs("markdown/r-references.bib")

r_citations <- cite_r(
  file = "markdown/r-references.bib",
  pkgs = c("papaja", "tidyverse", "knitr", "psych"),
  omit = FALSE,
  footnote = TRUE
  )

```


```{r setup-print-percent}
print_percent <- function(percent){
  apa_msg = papaja::apa_num(percent)
  final = paste0(apa_msg, " %")
  return(final)
}

print_freq_percent <- function(freq){
  percent = freq*100
  apa_msg = papaja::apa_num(percent)
  final = paste0(apa_msg, " %")
  return(final)
}


print_rel <- function(rel){
  return(paste0("$\alpha~=~", papaja::apa_num(rel), "$"))
}

print_cor <- function(cor){
  return(paste0("$r~=~", papaja::apa_num(cor), "$"))
}

print_icc <- function(icc){
  return(paste0("$ICC~=~", papaja::apa_num(icc), "$"))
}
```

<!-- Here we can incorporate child markdown-documents as the separate parts -->
# Introduction
something about the validity of big5 and g for job performance

something about need for assessment of big5 and g in job performance

something about cv being the first (and least costly) opportunity to assess big5

something about needing to figure out whether this can be done reliably and with sufficient validity, also highlighting that is is likely done already

here maybe (or one above) the previous findings

the present study aims to do this better in the following ways:
- use CVs from the general population
- also assess intelligence
- large sample, no training, real "zero shot" estimation

# Methods
```{r}
true_values <- read_excel("empra/cv_scores.xlsx")
colnames(true_values) <- as.character(true_values[1, ])

true_values_clean <- true_values[-1, ] %>%
  select(
    lebenslauf_id,
    age = age,
    education = education,
    gender = gender,
    work = work,
    wahre_Extraversion = extraversion,
    wahre_Vertraeglichkeit = agreeableness,
    wahre_Gewissenhaftigkeit = conscientiousness,
    wahrer_Neurotizismus = neuroticism,
    wahre_Offenheit = openness,
    wahre_Intelligenz = Total_sum
  ) %>%
  mutate(
    education = case_when(
      education == "Realschulsabschluss" ~ 1,
      education == "Ausbildung" ~ 2,
      education == "Abitur" ~ 3,
      education == "Bachelor" ~ 4,
      education == "Master" ~ 5,
      education == "Promotion" ~ 6,
    )
  )
```
We recruited a total of `r nrow(true_values_clean)` participants ($M_{age} =$ `r mean(as.numeric(true_values_clean$age)) %>% apa_num()`, $SD_{age} =$ `r sd(as.numeric(true_values_clean$age)) %>% apa_num()`, `r mean(true_values_clean$gender == "weiblich") %>% print_freq_percent()` female) who provided anonymized CVs to be rated. These participants were the subsample of a larger study collected at Heidelberg University who agreed to share their CV for the current work.

```{r}
s1_data <- read_excel("data/data_big-five-lebenslauf_2026-06-01_14-23.xlsx")
s2_data <- read_excel("data/data_cv_bewertung_2026-07-28_15-48.xlsx")

```

For Study 1, we recruited participants from a) the student population of Heidelberg University and b) an internet-based recruitment of German speakers on the platform Reddit. In total, we recruited `r nrow(s1_data)` participants ($M_{age} =$ `r mean(as.numeric(s1_data$SD02_01), na.rm = TRUE) %>% apa_num()`, $SD_{age} =$ `r sd(as.numeric(s1_data$SD02_01), na.rm = TRUE) %>% apa_num()`, `r mean(s1_data$SD01 == "1", na.rm = TRUE) %>% print_freq_percent()` female).

For Study 2, we recruited participants from a private university in Heidelberg (FOM). Here, students typically work in addition to their studies.. In total, we recruited `r nrow(s2_data)` participants ($M_{age} =$ `r mean(as.numeric(s2_data$SD02_01), na.rm = TRUE) %>% apa_num()`, $SD_{age} =$ `r sd(as.numeric(s2_data$SD02_01), na.rm = TRUE) %>% apa_num()`, `r mean(s2_data$SD01 == "1", na.rm = TRUE) %>% print_freq_percent()` female).

## Materials
To assess the personality of participants providing their CV, we used the german version of the Big Five Inventory 2 (BFI-2) [CITATION]. The BFI-2 consists of 12 likert-scale items per factor, 60 items total. It has previously shown consistently good reliability ($\alpha$ > 0.8) and validity [CITATION].

To assess the intelligence of participants providing their CV, we used the Intelligence-Structure-Test (IST) 2000-R [CITATION]. We only used the basic module ("Grundmodul") to assess fluid intelligence. This module consists of 9 subtests in three domains: verbal, numeric, and figural. It has demonstrated very good reliability $\alpha > 0.95$ and validity [CITATION liepmann].

The participants voluntarily provided their CVs and were instructed to provide them "as is" without adhering to a special format provided by the authors. CVs were subsequently anonymyzed by redacting any identifying information such as names, date of birth, company names, publication titles, or very specific job descriptions. In total, we received 25 CVs.

## Procedure
The participants providing their CV were part of a larger study (N = 200) that assessed the relationship between mental speed and intelligence. They completed the study in two sessions. In the first session, participants first completed memory tasks using EEG for about 2 hours, then they completed a questionnaire, including the BFI-2, finally, they completed 4 short working-memory tasks. The second session was conducted on another day by a trained experimenter and consisted of the IST, which required 90 minutes and then the Advanced Progressive Matrices [CITATION], which required 50 minutes. Results of the APM are not reported here. Following completion of the second session, participants were emailed and informed about the aim of the present study, the extent to which their CVs would be used and could volunteer to provide a CV which would be anonymized.

In Study 1, participants completed an online-survey on the hosting platform SoSciSurvey [CITATION]. They gave informed consent, and were asked to provide demographic information, experience with the Big Five personality model (yes/no) and experience with selection processes including CVs (scale of 1 - "no experience"  to 5 - "a lot of experience"). Then, we instructed the participants to inspect five CVs carefully and provide a rating of the person's personality. Personality raters were given on sliders from 0 to 100 with no numeric labels but verbal labels on both ends of the slider. These labels described the personality dimensions to be rated (see Table \@ref(tab:rating-scale-anchors)).

```{r rating-scale-anchors}
rating_labels <- data.frame(
  Dimension = c(
    "Extraversion",
    "Emotional Stability",
    "Conscientiousness",
    "Agreeableness",
    "Openness",
    "Intelligence"
  ),
  Left_Anchor_German = c(
    "zurückhaltend, reserviert",
    "selbstsicher, ruhig",
    "nachlässig, unsorgfältig",
    "wenig kooperativ, konfrontativ",
    "konservativ, vorsichtig",
    "wenig intelligent"
  ),
  Right_Anchor_German = c(
    "gesellig, kontaktfreudig, sozial",
    "emotional, verletzlich",
    "zuverlässig, sorgfältig",
    "kooperativ, freundlich",
    "neugierig, erfinderisch",
    "sehr intelligent"
  ),
  Left_Anchor_English = c(
    "reserved, withdrawn",
    "self-confident, calm",
    "careless, negligent",
    "uncooperative, confrontational",
    "conservative, cautious",
    "not very intelligent"
  ),
  Right_Anchor_English = c(
    "sociable, outgoing, social",
    "emotional, vulnerable",
    "reliable, conscientious",
    "cooperative, friendly",
    "curious, inventive",
    "very intelligent"
  ),
  check.names = FALSE
)

papaja::apa_table(
  rating_labels,
  caption = "Slider anchors used for personality and intelligence ratings."
)
```

Each CV was presented by itself with the rating sliders below and multi-choice question asking which criteria they used to make their decision (e.g. "Education", "Work experience and profile"). After participants rated 5 random CVs, they were asked whether they wanted to continue and rate five more CVs. This was possible up to a total of 15 CVs rated by each participant. 

Finally, participants indicated whether they payed attention during the survey and whether all of the CVs were presented without issues. Students of the University or the FOM could indicate that they wanted to receive course credits. No other rewards were issued. The median completion time for participants who viewed only five CVs was around 10 minutes.

The procedure was identical for Study 2, except that participants completed another, unrelated survey for about 10 minutes prior to the presented survey.

## Analysis
We estimated the reliability of ratings for each dimension (Big Five and Intelligence) separately using ICC(2) as implemented in the R package `psych` [@R-psych] to assess the absolute agreement of a single random rater. Based on this assessment and the Spearman-Brown prophecy formula, we provide the necessary number of raters whose average rating would achieve a reliability of 0.90. 

We estimated the accuracy of ratings in two ways. First, to assess the accuracy of only a single rater, we calculated the correlation across all CVs and raters between the rater's judgment and the underlying Big Five or intelligence score. Second, we average across all judgments for each CV and then calculated the correlation between average rating and underlying score.

# Results
```{r}
source("scripts/final_code.R")
source("scripts/final_code_s2.R")
```
We removed participants if they indicated that they were somewhat strongly or very strongly distracted during completion of the survey. Additionally, we removed participants who completed the entire survey in less than half of median completion time for participants who rated five CVs. Following data exclusion, $N =$ `r n_raters_final_cleaned_s1` participants remained in Study 1 and $N =$ `r n_raters_final_cleaned_s2` participants in Study 2. On average, each CV was judged by `r average_raters_per_cv_s1` participants in Study 1 and `r average_raters_per_cv_s2` participants in Study 2.

We provide an overview of descriptive information in Table A1 in the appendix.

```{r rel-overview-tab}
# Consolidate reliability estimates
overview_reliability_table = data.frame(
  construct = c("Extraversion", "Neuroticism", "Conscientiousness", "Agreeableness", "Openness", "Intelligence"),
  study_1 = 1:6,
  required_1 = 1:6,
  study_2 = 1:6,
  required_2 = 1:6
)

merkmale <- c("geschaetzte_Extraversion", "geschaetzter_Neurotizismus", "geschaetzte_Gewissenhaftigkeit", "geschaetzte_Vertraeglichkeit", "geschaetzte_Offenheit", "geschaetzer_IQ")
for (i in seq_along(merkmale)){
  merkmal = merkmale[i]
  
  icc_2_s1 = icc_ergebnisse_s1[[merkmal]]$ICC[2]
  required_s1 = required_raters(icc_2_s1, 0.90)
  icc_2_s1_lb = icc_ergebnisse_s1[[merkmal]]$`lower bound`[2]
  icc_2_s1_ub = icc_ergebnisse_s1[[merkmal]]$`upper bound`[2]
  
  s1_final = paste0(apa_num(icc_2_s1), " [", apa_num(icc_2_s1_lb), ", ", apa_num(icc_2_s1_ub), "]")
  
  icc_2_s2 = icc_ergebnisse_s2[[merkmal]]$ICC[2]
  required_s2 = required_raters(icc_2_s2, 0.90)
  icc_2_s2_lb = icc_ergebnisse_s2[[merkmal]]$`lower bound`[2]
  icc_2_s2_ub = icc_ergebnisse_s2[[merkmal]]$`upper bound`[2]
  
  s2_final = paste0(apa_num(icc_2_s2), " [", apa_num(icc_2_s2_lb), ", ", apa_num(icc_2_s2_ub), "]")
  
  overview_reliability_table$study_1[i] = s1_final
  overview_reliability_table$study_2[i] = s2_final
  overview_reliability_table$required_1[i] = required_s1
  overview_reliability_table$required_2[i] = required_s2
}

papaja::apa_table(
  overview_reliability_table,
  caption = "Interrater reliability of resume based judgments for big five and intelligence",
  note = "SOMETHING ABOUT THE TABLE COLUMN NAMES"
)
```

Table \@ref(tab:rel-overview-tab) provides an overview of the interrater reliability for the resume judgments. Highest reliability was observed for intelligence (Study 1: `r overview_reliability_table$study_1[which(overview_reliability_table$construct == "Intelligence")] %>% print_icc()`, Study 2: `r overview_reliability_table$study_2[which(overview_reliability_table$construct == "Intelligence")] %>% print_icc()`), followed by extraversion (Study 1: `r overview_reliability_table$study_1[which(overview_reliability_table$construct == "Extraversion")] %>% print_icc()`, Study 2: `r overview_reliability_table$study_2[which(overview_reliability_table$construct == "Extraversion")] %>% print_icc()`). The lowest reliability was observed for agreeableness in Study 1 (`r overview_reliability_table$study_1[which(overview_reliability_table$construct == "Agreeableness")] %>% print_icc()`) and openness in Study 2 (`r overview_reliability_table$study_2[which(overview_reliability_table$construct == "Openness")] %>% print_icc()`). The number of participants required to achieve good reliability of an average judgment ranged from `r min(c(overview_reliability_table$required_1, overview_reliability_table$required_2))` to `r max(c(overview_reliability_table$required_1, overview_reliability_table$required_2))`.

```{r acc-overview-tab}
paste_cor <- function(cor_test){
  paste0(apa_num(cor_test$estimate[[1]]), " [", apa_num(cor_test$conf.int[1]), ", ", apa_num(cor_test$conf.int[2]), "]")
}

# Consolidate reliability estimates
overview_accuracy_table = data.frame(
  construct = c("Extraversion", "Neuroticism", "Conscientiousness", "Agreeableness", "Openness", "Intelligence"),
  study_1 = c(
    paste_cor(accuracy_cor_extra_s1),
    paste_cor(accuracy_cor_neuro_s1),
    paste_cor(accuracy_cor_gewiss_s1),
    paste_cor(accuracy_cor_vertr_s1),
    paste_cor(accuracy_cor_offen_s1),
    paste_cor(accuracy_cor_iq_s1)
  ),
  avg_study_1 = c(
    average_data_cors_s1$Extraversion,
    average_data_cors_s1$Neurotizismus,
    average_data_cors_s1$Gewissenhaftigkeit,
    average_data_cors_s1$Vertraeglichkeit,
    average_data_cors_s1$Offenheit,
    average_data_cors_s1$IQ
  ), 
  study_2 = c(
    paste_cor(accuracy_cor_extra_s2),
    paste_cor(accuracy_cor_neuro_s2),
    paste_cor(accuracy_cor_gewiss_s2),
    paste_cor(accuracy_cor_vertr_s2),
    paste_cor(accuracy_cor_offen_s2),
    paste_cor(accuracy_cor_iq_s2)
  ),
  avg_study_2 = c(
    average_data_cors_s2$Extraversion,
    average_data_cors_s2$Neurotizismus,
    average_data_cors_s2$Gewissenhaftigkeit,
    average_data_cors_s2$Vertraeglichkeit,
    average_data_cors_s2$Offenheit,
    average_data_cors_s2$IQ
  )
)

papaja::apa_table(
  overview_accuracy_table,
  caption = "Accuracy of resume based judgments for big five and intelligence",
  note = "SOMETHING ABOUT THE TABLE COLUMN NAMES. PROVIDE THE N RATERS AND N CVS HERE ALSO"
)
```
Table \@ref(tab:acc-overview-tab) provides an overview of the accuracy of resume judgments. Highest accuracy was observed for intelligence (Study 1: `r overview_accuracy_table$study_1[which(overview_accuracy_table$construct == "Intelligence")] %>% print_cor()`, Study 2: `r overview_accuracy_table$study_2[which(overview_accuracy_table$construct == "Intelligence")] %>% print_cor()`), followed by neuroticism (Study 1: `r overview_accuracy_table$study_1[which(overview_accuracy_table$construct == "Neuroticism")] %>% print_cor()`), Study 2: (`r overview_accuracy_table$study_1[which(overview_accuracy_table$construct == "Neuroticism")] %>% print_cor()`). The lowest accuracy was observed for openness in both studies (Study 1: `r overview_accuracy_table$study_1[which(overview_accuracy_table$construct == "Openness")] %>% print_cor()`, Study 2: `r overview_accuracy_table$study_2[which(overview_accuracy_table$construct == "Openness")] %>% print_cor()`).

Accuracy improved for all judgments after averaging across raters for each CV. Here, the average intelligence rating correlated with actual intelligence at `r overview_accuracy_table$avg_study_1[which(overview_accuracy_table$construct == "Intelligence")] %>% print_cor()` in Study 1 and `r overview_accuracy_table$avg_study_2[which(overview_accuracy_table$construct == "Intelligence")] %>% print_cor()` in Study 2. Notably, intelligence judgments based on the resume provided incremental validity on actual intelligence over pure educational status of the resume's creator. Additional details on these models can be found in the appendix.

# Discussion


<!-- References -->
\newpage
# References
::: {#refs custom-style="Bibliography"}
:::

# Appendix

## Descriptive Information

## Testing incremental validity
Something about the data

something about the model

something about model comparison, something about their R2, something about the result of model comparison test
