---
title             : "Judging a book by its cover - investigating personality and intelligence judgments based on resumes (**WIP**)"
shorttitle        : "**WIP** Resume-based judgments"

author: 
  - name          : "Sven Lesche"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Hauptstraße 47-51, 69117 Heidelberg"
    email         : "sven.lesche@psychologie.uni-heidelberg.de"
    # role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
    #   - "Conceptualization"
    #   - "Writing - Original Draft Preparation"
    #   - "Writing - Review & Editing"
  - name          : "Valeria Maisch"
    affiliation   : "1"
    # role:
    #   - "Supervision"
  - name          : "Annika Leisse"
    affiliation   : "1"
    # role:
    #   - "Supervision"
  - name          : "Carolin Strauß"
    affiliation   : "1"
    # role:
    #   - "Supervision"
  - name          : "Nathalie Engelmann"
    affiliation   : "1"
    # role:
    #   - "Supervision"
  - name          : "Nele Pfründer"
    affiliation   : "1"
    # role:
    #   - "Supervision"
  - name          : "Tanja Bipp"
    affiliation   : "1"
    # role:
    #   - "Supervision"
    
affiliation:
  - id            : "1"
    institution   : "Ruprecht-Karls-University Heidelberg"
  - id            : "2"
    institution   : "Konstanz Business School"
  # add a second id using this syntax

authornote: |
  Author Notes go here.

abstract: |
  Personality and intelligence are important predictors of job performance. The present study examined whether these characteristics can be assessed at an early stage of the hiring process using only applicants’ resumes. We collected 25 resumes used in application processes from members of the general population and measured their personality and intelligence. Subsequently, two independent samples of 298 and 416 participants rated each applicant’s personality and intelligence based solely on the anonymized resumes.

  Across both samples, personality ratings by individual raters showed low inter-rater reliability (ICC = .11 - .22) and weak associations with applicants’ actual personality scores (r = .05 - .26). In contrast, intelligence ratings demonstrated higher inter-rater reliability (ICC = .35) and moderate predictive validity (r = .46). Averaging ratings across all raters for a given resume substantially improved reliability and increased predictive validity for both personality (up to r = .53) and intelligence (r = .77).
  
  These findings suggest that individual raters are generally unable to accurately infer personality from resumes, whereas intelligence can be estimated with greater accuracy. The improvement obtained by aggregating ratings indicates that resumes contain systematic information about these traits that can be extracted more reliably through collective judgment. 
 

keywords          : "personality, intelligence, resumes, personnel selection, judgment"
# wordcount         : "X"

bibliography      : ["r-references.bib", "cv-judgment.bib", "valeria-refs.bib"] # put your ref files here

floatsintext      : yes # for pics in text
linenumbers       : no
draft             : no
mask              : no

figurelist        : no
tablelist         : no
footnotelist      : no
link-citations    : true # custom addin, makes citations link to reference section
# figsintext        : yes # custom addin

classoption       : "man"
# the settings below allow compilation of APA7 style citations/documents
header-includes:
  - |
    \makeatletter
    \renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
      {-1em}%
      {\normalfont\normalsize\bfseries\typesectitle}}
    
    \renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
      {-\z@\relax}%
      {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
    \makeatother
  - | 
    \raggedbottom
  - |
    \usepackage{hhline}
  - |
    \setlength{\parskip}{0pt}

csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass     : "apa7"
output            : papaja::apa6_pdf
---
```{r setup, include = FALSE}
# Working directory
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

# disallow tables breaking over pages
knitr::opts_chunk$set(ft.keepnext = TRUE,
                      ft.align = "left",
                      ft.latex.float = "float")
# Seed for random number generation
set.seed(1234)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed) # this adds random seed to all chunks
knitr::opts_chunk$set(autodep = TRUE)
knitr::opts_chunk$set(message = FALSE)

knitr::dep_auto()
```

<!-- Setup -->
```{r setup-libraries}
# think about calling renv here to make sure everyone has the same packages installed
list.of.packages <- c("tidyverse", "rmarkdown", "papaja", "knitr", "psych")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

library(papaja)
library(tidyverse)
library(rmarkdown)
library(knitr)
library(psych)
library(readxl)

r_refs("markdown/r-references.bib")

r_citations <- cite_r(
  file = "markdown/r-references.bib",
  pkgs = c("papaja", "tidyverse", "knitr", "psych"),
  omit = FALSE,
  footnote = TRUE
  )

```

```{r setup-print-percent}
print_percent <- function(percent){
  apa_msg = papaja::apa_num(percent)
  final = paste0(apa_msg, " %")
  return(final)
}

print_freq_percent <- function(freq){
  percent = freq*100
  apa_msg = papaja::apa_num(percent)
  final = paste0(apa_msg, " %")
  return(final)
}


print_rel <- function(rel){
  return(paste0("$\alpha~=~", papaja::apa_num(rel), "$"))
}

print_cor <- function(cor){
  return(paste0("$r~=~", papaja::apa_num(cor), "$"))
}

print_icc <- function(icc){
  return(paste0("$ICC~=~", papaja::apa_num(icc), "$"))
}
```

In personnel selection processes, resumes often constitute the first source of information available to recruiters. As intelligence and personality are important indicators of job performance [@barrick_personality_2001; @sackett_contemporary_2024], recruiters make inferences about these characteristics from applicant resumes [@cole_using_2003; @derous_personality_2025; @roulin2013social] – yet the accuracy of these judgments remains poorly understood [@hartel_relationships_2024]. To contribute to a better understanding of this accuracy, we examined the validity of resume-based intelligence and personality inferences and whether aggregating ratings across multiple raters improves accuracy compared with individual judgments. We based our study on 25 resumes obtained from members of the general population, for whom personality and intelligence were assessed using standardized measures. Over 700 raters from two independent samples subsequently evaluated each applicant's Big-5 personality traits and intelligence solely from the anonymized resumes. This design allows us to determine how accurately resume ratings correspond to standardized assessments of intelligence and personality, and whether accuracy can be improved through collective judgments. Therefore, the study refines current knowledge on the accuracy of resume-based judgments, delineates the conditions under which they may be informative, and provides practical guidance on when additional sources of information are needed.

# Background
Although resumes are primarily designed to communicate relevant qualifications, they also contain cues that reflect personality or intelligence [@cole_using_2003; @derous_personality_2025; @hartel_relationships_2024]. Understanding how accurately intelligence and personality can be inferred from resumes is particularly important because resumes are a primary basis for screening decisions, and perceived intelligence and personality have been found to be substantially related to applicants’ perceived hireability and employability [@burns_effects_2014; @cole_recruiters_2009; @sinclair_does_2020].

Previous research on resume-based inferences has drawn on the Brunswikian lens model [@brunswik1956perception] as a theoretical framework [@derous_personality_2025] and found that resumes contain cues of personality and intelligence [@hartel_relationships_2024] that can be inferred with accuracy exceeding guessing levels [@cole_validity_2005; @frauendorfer_include_2015]. However, the overall predictive potential of resumes appears to be relatively limited, particularly for personality [@apers_are_2017; @cole_recruiters_2009; @hartel_relationships_2024]. Additionally, empirical investigations vary substantially in assessment procedures, resume materials, and rater samples, highlighting the need for methodologically rigorous assessments using a variety of actual resumes and replication across different rater samples.

Evidence regarding the accuracy of specific dimensions within the Five-Factor Model of personality [@costa1985neo] is mixed, with some studies finding greater accuracy for extraversion [@apers_are_2017; @cole_recruiters_2009], whereas others report greater accuracy for conscientiousness or openness to experience [@cole_validity_2005; @frauendorfer_include_2015; @hartel_relationships_2024]. Given these heterogeneous findings and methodological differences in previous research, we adopted an exploratory approach rather than formulating specific hypotheses for individual personality dimensions or intelligence. Using psychometrically validated measures of personality and intelligence and a range of authentic resumes, we examined the accuracy of resume-based judgments, whether accuracy could be improved through collective judgments, and whether our findings replicated across two independent samples.

# Methods
```{r}
true_values <- read_excel("empra/cv_scores.xlsx")
colnames(true_values) <- as.character(true_values[1, ])

true_values_clean <- true_values[-1, ] %>%
  select(
    lebenslauf_id,
    age = age,
    education = education,
    gender = gender,
    work = work,
    wahre_Extraversion = extraversion,
    wahre_Vertraeglichkeit = agreeableness,
    wahre_Gewissenhaftigkeit = conscientiousness,
    wahrer_Neurotizismus = neuroticism,
    wahre_Offenheit = openness,
    wahre_Intelligenz = Total_sum
  ) %>%
  mutate(
    education = case_when(
      education == "Realschulsabschluss" ~ 1,
      education == "Ausbildung" ~ 2,
      education == "Abitur" ~ 3,
      education == "Bachelor" ~ 4,
      education == "Master" ~ 5,
      education == "Promotion" ~ 6,
    )
  )
```
We recruited a total of `r nrow(true_values_clean)` participants ($M_{age} =$ `r mean(as.numeric(true_values_clean$age)) %>% apa_num()`, $SD_{age} =$ `r sd(as.numeric(true_values_clean$age)) %>% apa_num()`, `r mean(true_values_clean$gender == "weiblich") %>% print_freq_percent()` female) who provided anonymized resumes to be rated. These participants are a subsample of a larger study (N = 201) collected at a German University with an unrelated research question.

```{r}
s1_data <- read_excel("data/data_big-five-lebenslauf_2026-06-01_14-23.xlsx")
s2_data <- read_excel("data/data_cv_bewertung_2026-07-28_15-48.xlsx")

```

For Study 1, we recruited `r nrow(s1_data)` participants stemming from a) the student population of a German University, b) the general population of a German town using flyers, and c) an internet-based recruitment of German speakers on the platform Reddit ($M_{age} =$ `r mean(as.numeric(s1_data$SD02_01), na.rm = TRUE) %>% apa_num()`, $SD_{age} =$ `r sd(as.numeric(s1_data$SD02_01), na.rm = TRUE) %>% apa_num()`, `r mean(s1_data$SD01 == "1", na.rm = TRUE) %>% print_freq_percent()` female).

For Study 2, we recruited `r nrow(s2_data)` part-time students from a professional study program representing a primarily working sample ($M_{age} =$ `r mean(as.numeric(s2_data$SD02_01), na.rm = TRUE) %>% apa_num()`, $SD_{age} =$ `r sd(as.numeric(s2_data$SD02_01), na.rm = TRUE) %>% apa_num()`, `r mean(s2_data$SD01 == "1", na.rm = TRUE) %>% print_freq_percent()` female).

```{r}
source("scripts/final_code.R")
source("scripts/final_code_s2.R")
```

We removed participants if they indicated that they were somewhat strongly or very strongly distracted during completion of the online survey. Additionally, we removed participants who completed the entire survey in less than half of median completion time. After exclusion, final sample sizes consisted of $N =$ `r n_raters_final_cleaned_s1` participants for Study 1 and $N =$ `r n_raters_final_cleaned_s2` participants for Study 2. 

## Materials
To assess the personality of participants providing their resume, we used the german version of the Big Five Inventory 2 (BFI-2) [@dannerDeutscheVersionBig2016]. The BFI-2 consists of 12 likert-scale items per factor and has previously shown consistently good reliability ($\alpha$ > 0.8) and validity [@dannerDeutscheVersionBig2016]. Second, to assess fluid intelligence, we used the basic module ("Grundmodul") of the Intelligence-Structure-Test (IST) 2000-R [@liepmannIST]. It consists of 9 subtests in three domains: verbal, numeric, and figural. It has demonstrated very good reliability $\alpha > 0.95$ and validity [@liepmannIST].

The participants voluntarily provided their resumes and were instructed to provide them “as is” without adhering to a special format provided by the authors. They were given the option to either anonymize their resumes themselves or have the researchers do it for them. All resumes were fully anonymized by redacting any identifying information such as names, headshots, dates of birth, company names, publication titles, or very specific job descriptions.

## Procedure
The participants provided their resumes voluntarily and attended two assessment sessions on separate days. The first included the BFI-2, whereas the second contained the IST. 

For the resume-based judgments, a different set of participants completed an online-survey on the hosting platform SoSciSurvey [@leinert2024sosci]. The procedure was identical for both Study 1 and Study 2, except that the second sample completed another, unrelated survey for about 10 minutes prior to this survey.

First, all participants gave informed consent, and subsequently were asked to provide demographic information, experience with the Big Five personality model, and experience with selection processes including resumes. Then, we instructed the participants to inspect five resumes carefully and provide a rating of the person’s Big Five personality traits and intelligence. Ratings were given on sliders from 0 to 100 with no numeric labels but verbal labels in German on both ends of the slider. These labels described the personality dimensions to be rated (for a complete overview, see the electronic supplementary material; ESM). Each resume was presented on one page with rating sliders and a multiple-choice question below asking which criteria they used when forming their judgments (e.g. “Education”, “Work experience and profile”). After participants rated 5 random resumes, they were asked whether they wanted to continue and rate five more resumes. This was possible up to a total of 15 resumes for each participant. Finally, participants indicated whether they paid attention during the survey and whether all of the resumes were presented without technical issues. 
University students received course credits. No other rewards were issued. The median completion time for participants who viewed only five resumes was around 10 minutes.

## Analysis
We estimated the reliability of ratings for each dimension (Big Five and Intelligence) separately using ICC(2, 1) to assess the absolute agreement of a single random rater. Based on this assessment and the Spearman-Brown prophecy formula, we extrapolated the necessary number of raters whose average rating would achieve a reliability of 0.90.

We estimated the accuracy of ratings in two ways. First, to assess the accuracy of only a single rater, we calculated the correlation across all resumes and raters between the rater’s judgment and the underlying Big Five or intelligence score. Second, we averaged across all judgments for each resume and then calculated the correlation between average rating and underlying score. All analysis were conducted using `r r_citations$r`. All code and data necessary to reproduce this manuscript is available at **PROVIDE DOI here**.

# Results
On average, each resume was judged by `r average_raters_per_cv_s1` participants in Study 1 and `r average_raters_per_cv_s2` participants in Study 2. We provide an overview of descriptive information in the ESM.

```{r rel-overview-tab}
# Consolidate reliability estimates
overview_reliability_table = data.frame(
  construct = c("Extraversion", "Neuroticism", "Conscientiousness", "Agreeableness", "Openness", "Intelligence"),
  study_1 = 1:6,
  required_1 = 1:6,
  study_2 = 1:6,
  required_2 = 1:6
)

merkmale <- c("geschaetzte_Extraversion", "geschaetzter_Neurotizismus", "geschaetzte_Gewissenhaftigkeit", "geschaetzte_Vertraeglichkeit", "geschaetzte_Offenheit", "geschaetzer_IQ")
for (i in seq_along(merkmale)){
  merkmal = merkmale[i]
  
  icc_2_s1 = icc_ergebnisse_s1[[merkmal]]$ICC[2]
  required_s1 = required_raters(icc_2_s1, 0.90)
  icc_2_s1_lb = icc_ergebnisse_s1[[merkmal]]$`lower bound`[2]
  icc_2_s1_ub = icc_ergebnisse_s1[[merkmal]]$`upper bound`[2]
  
  s1_final = paste0(apa_num(icc_2_s1), " [", apa_num(icc_2_s1_lb), ", ", apa_num(icc_2_s1_ub), "]")
  
  icc_2_s2 = icc_ergebnisse_s2[[merkmal]]$ICC[2]
  required_s2 = required_raters(icc_2_s2, 0.90)
  icc_2_s2_lb = icc_ergebnisse_s2[[merkmal]]$`lower bound`[2]
  icc_2_s2_ub = icc_ergebnisse_s2[[merkmal]]$`upper bound`[2]
  
  s2_final = paste0(apa_num(icc_2_s2), " [", apa_num(icc_2_s2_lb), ", ", apa_num(icc_2_s2_ub), "]")
  
  overview_reliability_table$study_1[i] = s1_final
  overview_reliability_table$study_2[i] = s2_final
  overview_reliability_table$required_1[i] = required_s1
  overview_reliability_table$required_2[i] = required_s2
}

overview_reliability_table_print <- overview_reliability_table %>% 
  rename(
    "Construct" = construct,
    "ICC (Study 1)" = study_1,
    "ICC (Study 2)" = study_2,
    "k required (Study 1)" = required_1,
    "k required (Study 2)" = required_2
  )

papaja::apa_table(
  overview_reliability_table_print,
  caption = "Interrater reliability of resume based judgments for big five and intelligence",
    note = "Interrater reliability was estimated using the two-way random-effects intraclass correlation coefficient for absolute agreement, ICC(2,1). Values are reported with 95% confidence intervals. *k* required denotes the estimated number of raters required for the average rating to achieve a reliability of at least .90 according to the Spearman–Brown prophecy formula."
)
```

Table \@ref(tab:rel-overview-tab) provides an overview of the inter-rater reliability for the resume judgments. Highest reliability was observed for intelligence, followed by extraversion. The lowest reliability was observed for agreeableness in Study 1 and openness in Study 2. The number of participants required to achieve good reliability of an average judgment ranged from `r min(c(overview_reliability_table$required_1, overview_reliability_table$required_2))` to `r max(c(overview_reliability_table$required_1, overview_reliability_table$required_2))`.

```{r acc-overview-tab}
paste_cor <- function(cor_test){
  paste0(apa_num(cor_test$estimate[[1]]), " [", apa_num(cor_test$conf.int[1]), ", ", apa_num(cor_test$conf.int[2]), "]")
}

# Consolidate reliability estimates
overview_accuracy_table = data.frame(
  construct = c("Extraversion", "Neuroticism", "Conscientiousness", "Agreeableness", "Openness", "Intelligence"),
  study_1 = c(
    paste_cor(accuracy_cor_extra_s1),
    paste_cor(accuracy_cor_neuro_s1),
    paste_cor(accuracy_cor_gewiss_s1),
    paste_cor(accuracy_cor_vertr_s1),
    paste_cor(accuracy_cor_offen_s1),
    paste_cor(accuracy_cor_iq_s1)
  ),
  avg_study_1 = c(
    average_data_cors_s1$Extraversion,
    average_data_cors_s1$Neurotizismus,
    average_data_cors_s1$Gewissenhaftigkeit,
    average_data_cors_s1$Vertraeglichkeit,
    average_data_cors_s1$Offenheit,
    average_data_cors_s1$IQ
  ), 
  study_2 = c(
    paste_cor(accuracy_cor_extra_s2),
    paste_cor(accuracy_cor_neuro_s2),
    paste_cor(accuracy_cor_gewiss_s2),
    paste_cor(accuracy_cor_vertr_s2),
    paste_cor(accuracy_cor_offen_s2),
    paste_cor(accuracy_cor_iq_s2)
  ),
  avg_study_2 = c(
    average_data_cors_s2$Extraversion,
    average_data_cors_s2$Neurotizismus,
    average_data_cors_s2$Gewissenhaftigkeit,
    average_data_cors_s2$Vertraeglichkeit,
    average_data_cors_s2$Offenheit,
    average_data_cors_s2$IQ
  )
)

overview_accuracy_table_print <- overview_accuracy_table %>% 
  rename(
    "Single-rater r (Study 1)" = study_1,
    "Single-rater r (Study 2)" = study_2,
    "Mean-rating r (Study 1)" = avg_study_1,
    "Mean-rating r (Study 2)" = avg_study_2
  )

papaja::apa_table(
  overview_accuracy_table_print,
  caption = "Accuracy of resume based judgments for big five and intelligence",
  note = "Values are Pearson correlations (95% CIs) between resume-based judgments and the corresponding criterion scores (BFI-2 and IST 2000-R). Single-rater accuracy is based on individual judgments; mean-rating accuracy is based on ratings averaged across raters for each resume."
)
```

Table \@ref(tab:acc-overview-tab) provides an overview of the accuracy of resume judgments. Highest accuracy was observed for intelligence, followed by neuroticism. The lowest accuracy was observed for openness in both studies.Accuracy improved for all judgments after averaging across raters for each resume. Here, the average intelligence rating correlated with actual intelligence at `r overview_accuracy_table$avg_study_1[which(overview_accuracy_table$construct == "Intelligence")] %>% print_cor()` - `r overview_accuracy_table$avg_study_2[which(overview_accuracy_table$construct == "Intelligence")] %>% print_cor()` for both samples. Notably, resume-based intelligence judgments provided incremental validity on actual intelligence over applicants’ educational status in both studies, yielding around 16% additional variance explained (for additional information, see the ESM).

# Discussion

The present study aimed to determine how accurately resume-based judgments correspond to standardized assessments of intelligence and personality, and whether accuracy can be improved through collective judgments. Across two independent samples, we found that untrained raters showed low inter-rater reliability when inferring personality from resumes from members of the general population. Consistent with this, the accuracy of single-rater personality judgments was generally low, suggesting that resume-based personality impressions are unlikely to provide sufficiently valid information for personnel selection. In contrast, intelligence judgments showed higher reliability and were strongly associated with objectively measured intelligence.

These findings are broadly consistent with previous research, although the literature has been remarkably heterogeneous with respect to resume materials, raters, and assessment procedures. Studies using student resumes have generally reported low inter-rater agreement and weak criterion validity for Big Five judgments, with somewhat stronger performance for extraversion, conscientiousness, or openness [e.g. @apers_are_2017; @cole_recruiters_2009; @burns_effects_2014], and better accuracy for intelligence judgments [@cole_using_2003].

Averaging judgments across raters substantially improved both reliability and predictive accuracy for all constructs. Objectively measured scores correlated with averaged ratings of intelligence around $r > 0.75$ and personality up to $r = 0.53$. Notably, resume-based judgments provided incremental validity in predicting intelligence over applicants’ educational attainment. These findings indicate that resumes contain additional systematic information about applicants’ personality and intelligence. Consequently, the limitation in accuracy appears to lie less in the information contained in resumes and rather in single raters’ ability to extract it reliably. 

This raises the possibility that training recruiters to evaluate resumes more systematically may improve judgment accuracy [@cole_validity_2005]. Similarly, large language models show promise for extracting personality- and intelligence-related information from resumes [@grunenberg_machine_2024], although potential biases and other challenges of these systems need to be considered [@goretzko2022pitfalls; @kim2026algorithms].

A major strength of the present work is the use of real resumes paired with validated measures of both personality and intelligence. At the same time, the resume sample was intentionally heterogeneous and covered applicants with diverse educational and occupational backgrounds. Consequently, it remains unclear to what extent the present findings generalize to personnel selection within a single profession or for a specific job, where resumes may be considerably more homogeneous. Furthermore, our participants were untrained laypeople rather than professional recruiters. Even though @sinclair_does_2020 did not find improved accuracy for recruiters over laypeople in estimating intelligence, future studies should still investigate avenues such as recruiter training or machine learning to improve judgment quality.
Taken together, our findings suggest that first impressions based solely on resumes should be interpreted with caution, particularly when making inferences about applicants’ personality. While resumes appear to contain meaningful information about intelligence, reliable personality assessment is unlikely to be achieved through unaided human judgment alone.


<!-- References -->
\newpage
# References
::: {#refs custom-style="Bibliography"}
:::

# Appendix

```{r rating-scale-anchors}
rating_labels <- data.frame(
  Construct = c(
    "Extraversion",
    "Neuroticism",
    "Conscientiousness",
    "Agreeableness",
    "Openness",
    "Intelligence"
  ),
  `Left Anchor (German)` = c(
    "zurückhaltend, reserviert",
    "selbstsicher, ruhig",
    "nachlässig, unsorgfältig",
    "wenig kooperativ, konfrontativ",
    "konservativ, vorsichtig",
    "wenig intelligent"
  ),
  `Right Anchor (German)` = c(
    "gesellig, kontaktfreudig, sozial",
    "emotional, verletzlich",
    "zuverlässig, sorgfältig",
    "kooperativ, freundlich",
    "neugierig, erfinderisch",
    "sehr intelligent"
  ),
  `Left Anchor (English)` = c(
    "reserved, withdrawn",
    "self-confident, calm",
    "careless, negligent",
    "uncooperative, confrontational",
    "conservative, cautious",
    "not very intelligent"
  ),
  `Right Anchor (English)` = c(
    "sociable, outgoing, social",
    "emotional, vulnerable",
    "reliable, conscientious",
    "cooperative, friendly",
    "curious, inventive",
    "very intelligent"
  ),
  check.names = FALSE
)

papaja::apa_table(
  rating_labels,
  caption = "Slider anchors used for personality and intelligence ratings.",
  note = "Slider anchors were presented in German. English translation is only to improve readibility of the manuscript and not an authorative translation of slider anchors."
)
```

## Descriptive Information
```{r descriptive-tab}
overview_descriptives <- bind_rows(
  lebenslauf_tabelle %>% mutate(Source = "True sample"),
  avg_judgments_s1 %>% mutate(Source = "Study 1"),
  avg_judgments_s2 %>% mutate(Source = "Study 2")
) %>%
  mutate(
    Construct = case_when(
      grepl("Extraversion", Merkmal) ~ "Extraversion",
      grepl("Neurotizismus", Merkmal) ~ "Neuroticism",
      grepl("Gewissenhaftigkeit", Merkmal) ~ "Conscientiousness",
      grepl("Vertraeglichkeit", Merkmal) ~ "Agreeableness",
      grepl("Offenheit", Merkmal) ~ "Openness",
      grepl("IQ|Intelligenz", Merkmal) ~ "Intelligence"
    )
  ) %>%
  transmute(
    Construct,
    Source,
    Summary = sprintf("%.2f (%.2f), n = %d", Mittelwert, SD, n)
  ) %>%
  pivot_wider(
    names_from = Source,
    values_from = Summary
  ) %>%
  arrange(factor(
    Construct,
    levels = c(
      "Extraversion",
      "Neuroticism",
      "Conscientiousness",
      "Agreeableness",
      "Openness",
      "Intelligence"
    )
  ))

papaja::apa_table(
  overview_descriptives,
  caption = "Descriptive statistics for personality and intelligence scores in the target sample and resume-based judgments across both studies.",
  note = "Values are means with standard deviations in parentheses; the number of observations is reported after each value. Target-sample scores are based on self-reports (BFI-2) and performance on the IST 2000-R. Resume-based judgments were rescaled from the original 0–100 slider to a 1–5 scale to facilitate comparison with the BFI-2. Intelligence scores in the target sample represent the number of correctly solved items on the IST 2000-R. The average number of correctly solved items (111) corresponds to an IQ of 106."
)
```


## Testing incremental validity

To examine whether resume-based intelligence judgments provide information beyond educational attainment, we estimated two nested linear regression models using the average intelligence judgment for each resume. The analysis was conducted at the resume level (*N* = 25), with the criterion being the target person's intelligence score obtained from the IST 2000-R.

The baseline model included educational attainment as the sole predictor. The extended model additionally included the mean resume-based intelligence judgment.

To evaluate the incremental validity of resume-based judgments, the two nested models were compared using an F-test. Model fit was summarized using the coefficient of determination ($R^2$) for each model. Incremental validity was assessed by the increase in explained variance ($\Delta R^2$) and the significance of the nested model comparison. A significant improvement in model fit indicates that resume-based intelligence judgments explain unique variance in intelligence beyond educational attainment alone.

```{r, results = "asis", echo = FALSE}
# Study 1
m1_r2_s1 <- summary(m1_s1)$r.squared
m2_r2_s1 <- summary(m2_s1)$r.squared
comp_s1  <- anova(m1_s1, m2_s1)

# Study 2
m1_r2_s2 <- summary(m1_s2)$r.squared
m2_r2_s2 <- summary(m2_s2)$r.squared
comp_s2  <- anova(m1_s2, m2_s2)

p_value_s1 <- comp_s1$`Pr(>F)`[2]
p_value_s2 <- comp_s2$`Pr(>F)`[2]

```

### Study 1

The baseline model, including educational attainment as the sole predictor, explained `r apa_num(m1_r2_s1 * 100, digits = 1)`% of the variance in intelligence ($R^2$ = `r apa_num(m1_r2_s1)`). Adding the mean resume-based intelligence judgment increased the explained variance to `r apa_num(m2_r2_s1 * 100, digits = 1)`% ($R^2$ = `r apa_num(m2_r2_s1)`), corresponding to an increase of $\Delta R^2 =$ `r apa_num(m2_r2_s1 - m1_r2_s1)`.

The comparison of the nested models indicated that the extended model provided a significantly better fit than the baseline model *F*(`r comp_s1$Df[2]`, `r comp_s1$Res.Df[2]`) = `r apa_num(comp_s1$F[2])`, *p* `r papaja::apa_p(p_value_s1)`.

### Study 2

The baseline model, including educational attainment as the sole predictor, explained `r apa_num(m1_r2_s2 * 100, digits = 1)`% of the variance in intelligence ($R^2$ = `r apa_num(m1_r2_s2)`). Adding the mean resume-based intelligence judgment increased the explained variance to `r apa_num(m2_r2_s2 * 100, digits = 1)`% ($R^2$ = `r apa_num(m2_r2_s2)`), corresponding to an increase of $\Delta R^2 =$ `r apa_num(m2_r2_s2 - m1_r2_s2)`.

The comparison of the nested models indicated that the extended model provided a significantly better fit than the baseline model *F*(`r comp_s2$Df[2]`, `r comp_s2$Res.Df[2]`) = `r apa_num(comp_s2$F[2])`, *p* `r papaja::apa_p(p_value_s2)`.