---
title             : "Some Long Title - Maybe something more specific"
shorttitle        : "Short Title"

author: 
  - name          : "Author 1"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Street Str. 1"
    email         : "author.one@mail.com"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - "Conceptualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - name          : "Author 2"
    affiliation   : "2"
    role:
      - "Supervision"

affiliation:
  - id            : "1"
    institution   : "Ruprecht-Karls-University Heidelberg"
  - id            : "2"
    institution   : "Konstanz Business School"
  # add a second id using this syntax

authornote: |
  Author Notes go here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  
  One or two sentences to put the results into a more **general context**.
  
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keyword, more keyword, crazy keyword"
wordcount         : "X"

# bibliography      : ["r-references.bib"] # put your ref files here

floatsintext      : yes # for pics in text
linenumbers       : no
draft             : no
mask              : no

figurelist        : no
tablelist         : no
footnotelist      : no
link-citations    : true # custom addin, makes citations link to reference section
# figsintext        : yes # custom addin

classoption       : "man"
# the settings below allow compilation of APA7 style citations/documents
header-includes:
  - |
    \makeatletter
    \renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
      {-1em}%
      {\normalfont\normalsize\bfseries\typesectitle}}
    
    \renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
      {-\z@\relax}%
      {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
    \makeatother
  - | 
    \raggedbottom
  - |
    \usepackage{hhline}
  - |
    \setlength{\parskip}{0pt}

csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass     : "apa7"
output            : papaja::apa6_pdf
---
```{r setup, include = FALSE}
# Working directory
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

# disallow tables breaking over pages
knitr::opts_chunk$set(ft.keepnext = TRUE,
                      ft.align = "left",
                      ft.latex.float = "float")
# Seed for random number generation
set.seed(1234)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed) # this adds random seed to all chunks
knitr::opts_chunk$set(autodep = TRUE)
knitr::dep_auto()
```

<!-- Setup -->
```{r setup-libraries}
# think about calling renv here to make sure everyone has the same packages installed
list.of.packages <- c("tidyverse", "rmarkdown", "papaja", "knitr", "brms", "rstan", "cmdstanr")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

library(papaja)
library(tidyverse)
library(rmarkdown)
library(knitr)
library(acdcquery)

r_refs("markdown/r-references.bib")

r_citations <- cite_r(
  file = "markdown/r-references.bib",
  pkgs = c("papaja", "tidyverse", "knitr", "acdcquery", "cmdstanr", "rstan", "brms"),
  omit = FALSE,
  footnote = TRUE
  )

```


```{r setup-print-percent}
print_percent <- function(percent){
  apa_msg = papaja::apa_num(percent)
  final = paste0(apa_msg, " %")
  return(final)
}

print_freq_percent <- function(freq){
  percent = freq*100
  apa_msg = papaja::apa_num(percent)
  final = paste0(apa_msg, " %")
  return(final)
}


print_rel <- function(rel){
  return(paste0("$\alpha~=~", papaja::apa_num(rel), "$"))
}

print_icc <- function(icc){
  return(paste0("$ICC~=~", papaja::apa_num(icc), "$"))
}
```

```{r}
source("")
```


<!-- Here we can incorporate child markdown-documents as the separate parts -->
# Introduction
something about the validity of big5 and g for job performance

something about need for assessment of big5 and g in job performance

something about cv being the first (and least costly) opportunity to assess big5

something about needing to figure out whether this can be done reliably and with sufficient validity, also highlighting that is is likely done already

here maybe (or one above) the previous findings

the present study aims to do this better in the following ways:
- use CVs from the general population
- also assess intelligence
- large sample, no training, real "zero shot" estimation

# Methods
Participants for CV

Participants for Estimation
- study 1 
- study 2

CV materials, describe range and anonymization protocoll

procedure, how were people asked to rank (also with what scales)

analysis: how are we assessing reliability, how are we quantifying validity

# Results
ICC estimates

validity estimates, single subject and average

# Discussion


<!-- References -->
\newpage
# References
::: {#refs custom-style="Bibliography"}
:::

